### 2017-12-29 icde/revision/sec-alg.tex

To verify this observation, we also collect the statistics of citation/venue graphs and Web graphs illustrated in Table~\ref{tab-batch}, where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}, \markedb{and numbers $x/y$ in the first three rows are the corresponding statistics on citation/venue graphs.}
Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the \scc edge ratios $|E_i|/|E|$ are greater than 59\%. In contrast, the \sccs in citation and venue graphs are quite small as a result of the {\em temporal order of citations}, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
%
This specific structure in scholarly data has been long ignored in the past literature, which indeed has a positive impact on computations. Taking $t=100$ for example, algorithm \twprscc only needs to scan $4|E|$ edges on citation and venue graphs, but over $59|E|$ edges on Web graphs.

>>>>

To verify this observation, we also collect the statistics of citation/venue graphs and Web graphs illustrated in Table~\ref{tab-batch}, where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}.
Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the \scc edge ratios $|E_i|/|E|$ are greater than 59\%. In contrast, the \sccs in citation and venue graphs are quite small as a result of the {\em temporal order of citations}, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
%
This specific structure in scholarly data has been long ignored in the past literature, which indeed has a positive impact on computations. Taking $t=100$ for example, algorithm \twprscc only needs to scan $4|E|$ edges on citation and venue graphs, but over $59|E|$ edges on Web graphs.

### 2017-12-29 icde/revision/sec-incAlg.tex

Let $G_A=(V_A,E_A)$, $G_B=(V_B,E_B)$ and $G_C=(V_C,E_C)$, respectively, and
let $E_{AB}$ and $E_{CB}$  be the sets of edges from $G_A$ to $G_B$ and from $G_C$ to $G_B$, respectively.
In this way, graph $G^+$ is divided into subgraphs $\{G_A$, $G_B$, $G_C\}$ and edge sets $\{E_{AB}, E_{CB}\}$.
%
We then have $G^+[\Delta V]$ = $G_C$, $\Delta E$ = $E_C\cup E_{CB}$, $V$ = $V_A\cup V_B$ and $E$ = $E_A\cup E_B\cup E_{AB}$.

>>>>

Let $G_A=(V_A,E_A)$, $G_B=(V_B,E_B)$ and $G_C=(V_C$, $E_C)$, respectively, and
let $E_{AB}$ and $E_{CB}$  be the sets of edges from $G_A$ to $G_B$ and from $G_C$ to $G_B$, respectively.
In this way, graph $G^+$ is divided into subgraphs $\{G_A$, $G_B$, $G_C\}$ and edge sets $\{E_{AB}, E_{CB}\}$.
%
We then have $G^+[\Delta V]$ = $G_C$, $\Delta E$ = $E_C\cup E_{CB}$, $V$ = $V_A\cup V_B$ and $E$ = $E_A\cup E_B\cup E_{AB}$.

### 2017-12-29 icde/revision/sec-intro.tex

Scholarly articles are involved with multiple entities such as authors, venues, dates and references. That is, scholarly article ranking is essentially a problem of assessing the importance of nodes in a heterogeneous network.
However, effective and efficient ranking of nodes in such a large complex network is a different task due to the heterogeneous, evolving and dynamic natures of involved entities~\cite{AggarwalS14-survey,fcs-biggraph}.

@@

Query independent ranking of scholarly articles remains difficult~\cite{wsdmcup}, although there exists quite a bit of work on scholarly article ranking, \eg~\cite{Garfield471,Liang16AAAI,Jiang12-MRank,Waltman2014}.
Most previous work exploits the time-dependent information of scholarly data in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, which fails to capture the diverse citation patterns of individual articles~\cite{Chakraborty15}.
Further, to our knowledge, little concern has been paid to dynamic scholarly article ranking except \cite{GhoshKHLL11} with a strong and impractical assumption that there are no citations between articles published in the same years.
%\marked{Finally, the bias caused by the dynamic nature of data has never been exploited in scholarly article ranking}.

@@

\sstab(1) We first  propose a \underline{S}cholarly \underline{A}rticle \underline{Rank}ing model, referred to as \ensemblerank, by assembling the importance of three classes of entities (articles, venues and authors) for scholarly article ranking (Section \ref{sec-model}).
%
The importance is a combination of {\em prestige} and {\em popularity} to capture the evolving nature of entities.
%
To compute the prestige of articles and venues, we propose a novel {\em Time-Weighted PageRank} with a time decaying factor based on the citation statistics (instead of simple exponential decay), and the prestige of authors is the average prestige of all their published articles.
%
The popularity of an article is the sum of all its citation freshness (how close to the current year), while the one of venues and authors is the average popularity of their associated articles.
%
%Observe that (a), intuitively, prestige favors articles with many citations soon after their publication, and popularity favors those with recent citations, and (b) both prestige and popularity capture the evolving nature of entities.
%
To our knowledge, the Time-Weighted PageRank is among the first to incorporate the diverse citation patterns of individual articles \markedb{and exploit citation statistics for scholarly article ranking.}
%and the long-term bias caused by the dynamic nature of data

\sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank \markedb{and show its efficiency advantage in terms of an analysis of the citation characteristics and a specific structural property of scholarly graphs.}
%in which we propose a block-wise method for Time-Weighted PageRank in terms of an analysis of the citation characteristics of scholarly articles.

@@

%All the detailed proofs can be found in \cite{SARank-full}.
All the proofs can be found in \cite{SARank-full}.

>>>>

Scholarly articles are involved with multiple entities such as authors, venues, dates and references. That is, scholarly article ranking is essentially a problem of assessing the importance of nodes in a heterogeneous network.
However, effective and efficient ranking of nodes in such a large complex network is a difficult task due to the heterogeneous, evolving and dynamic natures of involved entities~\cite{AggarwalS14-survey,fcs-biggraph}.

@@

Query independent ranking of scholarly articles remains challenging~\cite{wsdmcup}, although there exists quite a bit of work on scholarly article ranking, \eg~\cite{Garfield471,Liang16AAAI,Jiang12-MRank,Waltman2014}.
Most previous work exploits the time-dependent information of scholarly data in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, which fails to capture the diverse citation patterns of individual articles~\cite{Chakraborty15}.
Further, to our knowledge, little concern has been paid to dynamic scholarly article ranking except \cite{GhoshKHLL11} with a strong and impractical assumption that there are no citations between articles published in the same years.
%\marked{Finally, the bias caused by the dynamic nature of data has never been exploited in scholarly article ranking}.

@@

\sstab(1) We first  propose a \underline{S}cholarly \underline{A}rticle \underline{Rank}ing model, referred to as \ensemblerank, by assembling the importance of three classes of entities (articles, venues and authors) for scholarly article ranking (Section \ref{sec-model}).
%
The importance is a combination of {\em prestige} and {\em popularity} to capture the evolving nature of entities.
%
To compute the prestige of articles and venues, we propose a novel {\em Time-Weighted PageRank} with a time decaying factor based on the citation statistics (instead of simple exponential decay), and the prestige of authors is the average prestige of all their published articles.
%
The popularity of an article is the sum of all its citation freshness (how close to the current year), while the one of venues and authors is the average popularity of their associated articles.
%
%Observe that (a), intuitively, prestige favors articles with many citations soon after their publication, and popularity favors those with recent citations, and (b) both prestige and popularity capture the evolving nature of entities.
%
To our knowledge, our Time-Weighted PageRank is among the first to incorporate diverse citation patterns of individual articles and to exploit citation statistics for scholarly article ranking.
%and the long-term bias caused by the dynamic nature of data

\sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank %\markedb{and show its efficiency advantage in terms of an analysis of the citation characteristics and a specific structural property of scholarly graphs.}
in which we propose a block-wise method for Time-Weighted PageRank in terms of an analysis of the citation characteristics of scholarly articles.

@@

All the detailed proofs can be found in \cite{SARank-full}.
%All the proofs can be found in \cite{SARank-full}.

### 2017-12-29 icde/revision/sec-model.tex

In this section, we first present Time-Weighted PageRank for evaluating  the importance of entities, defined as a combination of the prestige and popularity, and then introduce our ranking model \ensemblerank that assembles the importance of articles, venues and authors involved in scholarly articles.
%
\markedb{Before going into details, it is worthy pointing out that although this work focuses on query independent ranking, it can also be used for query dependent ranking. Our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores.}

@@

\stitle{Time-Weighted PageRank (TWPageRank)}. Most previous work simply exploits temporal information in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}. We rethink the usage of time information in terms of the impacts of scholarly articles.
Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with a single citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years   (but not the last year) after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1. Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
% In general,
\markedb{Inspired by these citation patterns,} {\em the impact of an article tends to decay with time after the peak time only}~\cite{WangSB13}. That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
%Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
Also observe that {\em each individual article has its own peak time} as articles may reach their citation peaks in different patterns and time.
%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.

@@

\begin{figure}
\centering
\hspace{-4ex}
\subfigure{\label{fig-paper}
\includegraphics[scale=0.41]{fig/yearly-papers.eps}}
\hspace{-4ex}
\subfigure{\label{fig-citation}
\includegraphics[scale=0.41]{fig/yearly-references.eps}}
\caption{\small Statistics of scholarly articles that reports the {\em logscale percentage of the number of papers (left) and citations (right) of each year} \wrt\ the total number of papers and citations on \aan, \aminer and \magdata, respectively.}
\label{fig-data-analysis}
\vspace{-3ex}
\end{figure}
%[{\scriptsize a}] [{\scriptsize b}]

@@

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-twpr}
PR(v)=d\sum_{(u,v)\in E} \frac{w(u,v)PR(u)}{W(u)}+\frac{1-d}{n},
\end{equation}
\end{small}
%
\noindent where $PR(u)$ and $PR(v)$ are the TWPageRank scores of $u$ and $v$, respectively, $E$ is the set of edges, $W(u)=\Sigma_{v} w(u,v)$ is the sum of the impact weights on all edges from $u$, $n$ is the number of nodes and $d$ is a damping parameter in $(0, 1)$. By Eq.~(\ref{eq-twpr}), we can see that prestige is updated based on the impact weights, not equally distributed.

@@

\eat{
\begin{proof}
It is known that a sequence of vectors $x^{(k)}$ such that $x^{(k+1)}=A\cdot x^{(k)}+b$ (where $k=0,1,\dots$) converges to a unique vector $x^*$,  regardless of the initial vector $x^0$, if and only if $\rho(A)<1$~\cite{kelley1999iterative}, where $\rho(A)$ is the spectral radius of matrix $A$. Hence, it suffices to show $\rho(d\cdot M^T) < 1$ by Eq.~(\ref{eq-twpr-update}).

@@

\vspace{-1ex}
\stitle{Remarks}.
\markedb{
The goal of our TWPageRank is to change node values, \ie importance. One may wonder why not directly change node values. However, it is difficult to handle as importance does not have a clear and closed-form definition and it may also cause problems for convergence.
To our knowledge, there is no related work on changing node weights and it is yet unclear how to handle it. Finally, we use impact weights to achieve the goal since importance is essentially propagable through edges and it is also fair for all nodes.
}

@@

A {\em citation graph} $G^c(V^c, E^c)$ is firstly constructed using the citation information such that (a) a node in $V^c$ denotes an article, (b) a directed edge $(u,v)$ in $E^c$ denotes that $u$ cites $v$, and (c) each node is associated with two types of time information: the publication year and the latest year having the largest (logscale) number of citations.

@@

%However, the resulting author citation graph to compute the prestige is typically too large to handle.
\markedb{To do this, an {\em author citation graph} needs to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$. It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches to 7.12  billion on the largest \magdata (\ie the memory cost of storage only is 57GB). It is computationally expensive to compute prestige of authors with TWPageRank on that graph.}
Hence, we evaluate the prestige of an author, by using the average prestige of all articles published by the author. Similar to the venue component, the popularity of an author is also defined as the average popularity of her/his published articles. Finally, the prestige and popularity are combined to derive the importance in the same way as the citation component.

@@

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-ensemble}
R(v) =  \alpha R_c(v) + \beta R_v(v) + (1 - \alpha - \beta) R_a(v).
\end{equation}
\end{small}
\noindent Here aggregating parameters $\alpha$ and $\beta$ and value $(1 - \alpha - \beta)$ regularize the contributions of the citation, venue and author information.
%
\markedb{
By this, our model is able to fit to the various ranking scenarios in real-life applications, which hardly can be covered with one set of parameters. As will be shown in the experiments, our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range, \ie $[0,1]$. }
%Intuitively, these parameters indicate the intensity of the correlation between the importance of scholarly articles and the specific information.

>>>>

In this section, we first present Time-Weighted PageRank for evaluating  the importance of entities, defined as a combination of the prestige and popularity, and then introduce our ranking model \ensemblerank that assembles the importance of articles, venues and authors involved in scholarly articles.
%
%\markedb{Before going into details, it is worthy pointing out that although this work focuses on query independent ranking, it can also be used for query dependent ranking. Our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores.}

@@

\stitle{Time-Weighted PageRank (TWPageRank)}. Most previous work simply exploits temporal information in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}. We rethink the usage of time information in terms of the impacts of scholarly articles.
Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with a single citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years   (but not the last year) after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1. Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent but not simply in the form of exponential decay that only considers  the case of {\em MonDec}.
%
To unify these distinct citation patterns, we adopt that {\em the impact of an article tends to decay with time after the peak time}, as pointed out in~\cite{WangSB13}. That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the (highest) peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
%Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
Also observe that {\em each individual article has its own peak time} as articles may reach their citation peaks in different patterns and time.
%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.

@@

\begin{figure}
\centering
\hspace{-4ex}
\subfigure{\label{fig-paper}
\includegraphics[scale=0.41]{fig/yearly-papers.eps}}
\hspace{-4ex}
\subfigure{\label{fig-citation}
\includegraphics[scale=0.41]{fig/yearly-references.eps}}
\caption{\small Statistics of scholarly articles: (1) the (logscale) percentage of papers in each year \wrt\ all papers (left) and (2) the (logscale) percentage of citations in each year \wrt\ all citations (right) on datasets \aan, \aminer and \magdata, respectively.}
\label{fig-data-analysis}
\vspace{-3ex}
\end{figure}
%[{\scriptsize a}] [{\scriptsize b}]

@@

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-twpr}
PR(v)=d\sum_{(u,v)\in E} \frac{w(u,v)PR(u)}{W(u)}+\frac{1-d}{n},
\end{equation}
\end{small}
where $PR(u)$ and $PR(v)$ are the TWPageRank scores of $u$ and $v$, respectively, $E$ is the set of edges, $W(u)=\Sigma_{v} w(u,v)$ is the sum of the impact weights on all edges from $u$, $n$ is the number of nodes and $d$ is a damping parameter in $(0, 1)$. By Eq.~(\ref{eq-twpr}), we can see that prestige is updated based on the impact weights, not equally distributed.

@@

\eat{%%%%%%%
\begin{proof}
It is known that a sequence of vectors $x^{(k)}$ such that $x^{(k+1)}=A\cdot x^{(k)}+b$ (where $k=0,1,\dots$) converges to a unique vector $x^*$,  regardless of the initial vector $x^0$, if and only if $\rho(A)<1$~\cite{kelley1999iterative}, where $\rho(A)$ is the spectral radius of matrix $A$. Hence, it suffices to show $\rho(d\cdot M^T) < 1$ by Eq.~(\ref{eq-twpr-update}).

@@

%\vspace{-1ex}
%\stitle{Remarks}.
%\markedb{
%The goal of our TWPageRank is to change node values, \ie importance. One may wonder why not directly change node values. However, it is difficult to handle as importance does not have a clear and closed-form definition and it may also cause problems for convergence.
%To our knowledge, there is no related work on changing node weights and it is yet unclear how to handle it. Finally, we use impact weights to achieve the goal since %importance is essentially propagable through edges and it is also fair for all nodes.
%}

@@

A {\em citation graph} $G^c(V^c, E^c)$ is firstly constructed using the citation information such that (a) a node in $V^c$ denotes an article, (b) a directed edge $(u,v)$ in $E^c$ denotes that $u$ cites $v$, and (c) each node is associated with two types of time information: the publication year and the latest year having the largest scaled number of citations.

@@

%However, the resulting author citation graph to compute the prestige is typically too large to handle.
One way to do this is to construct an author citation graph  such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$. However, it is easy to see that all authors of a article forms a clique, which makes it computationally expensive to compute the prestige of authors on such an author citation graph with TWPageRank.

Hence, we choose to evaluate the prestige of an author with the average prestige of all articles published by the author. Similar to the venue component, the popularity of an author is  defined as the average popularity of her/his published articles. Finally, the prestige and popularity are combined to derive the importance along the same way as the citation component.

@@

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-ensemble}
R(v) =  \alpha R_c(v) + \beta R_v(v) + (1 - \alpha - \beta) R_a(v).
\end{equation}
\end{small}
\noindent Here aggregating parameters $\alpha$ and $\beta$ and value $(1 - \alpha - \beta)$ regularize the contributions of the citation, venue and author information,
which make our model be able to fit to the various ranking scenarios. As will be seen in the experiments, our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range.
Intuitively, these parameters indicate the intensity of the correlation between the importance of scholarly articles and the specific information.

### 2017-12-29 icde/revision/sec-related.tex

PageRank \cite{Brin98:PageRank} and its extensions have been extensively used for citation analyses \cite{Waltman2014}. While PageRank equally propagates scores along outlinks, Weighted PageRank extends PageRank by distributing scores based on certain criteria such as popularity of pages~\cite{Xing04:WPR} or authority of authors~\cite{Ding11}.
%Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking.
\markedb{Scholarly graph is a kind of temporal graphs~\cite{temporalgraph} and temporal information is a key factor for scholarly article ranking.}
There has been work extending temporal information into PageRank, \eg exponentially decayed weights~\cite{Li08TSRanking}, exponentially decayed initial vectors~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}.
%Different from previous work,
Differently, our Time-Weighted PageRank \markedb{is inspired by an analysis of impacts of articles} and discriminately propagates scores in terms of statistics of citations.

%\stitle{Dynamic algorithms}.
Dynamic algorithms have proven useful for various tasks by avoiding computing from scratch~\cite{RamalingamR93}.
To our knowledge, little concern has been paid to dynamic scholarly article ranking except that~\cite{GhoshKHLL11} uses PageRank in dynamic citation networks. However, its solution is based on a strong and impractical assumption that there are no citations between articles in the same years.
Further, although there exist several studies on incremental PageRank computation~\cite{DesikanPSK05,AbiteboulPC03,WuR09} and on incremental PageRank approximation \cite{BahmaniCG10,BahmaniKMU12}, they are not designed for scholarly article ranking.
%
\markedb{In this work, we study dynamic scholarly article ranking in the general case and develop our incremental algorithm based on the citation characteristics, which has never been exploited before.}
%Different from previous work, we study scholarly article ranking in a dynamic environment in terms of the citation characteristics of scholarly articles, which has never been exploited before.

>>>>

PageRank \cite{Brin98:PageRank} and its extensions have been extensively used for citation analyses \cite{Waltman2014}. While PageRank equally propagates scores along outlinks, Weighted PageRank extends PageRank by distributing scores based on certain criteria such as popularity of pages~\cite{Xing04:WPR} or authority of authors~\cite{Ding11}.
%Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking.
Scholarly graphs belong to temporal graphs~\cite{temporalgraph}, and temporal information is a key factor for scholarly article ranking.
There has been work extending temporal information into PageRank, \eg exponentially decayed weights~\cite{Li08TSRanking}, exponentially decayed initial vectors~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}.
%Different from previous work,
Differently, our Time-Weighted PageRank is designed based on a deep analysis of scholarly articles, and discriminately propagates scores in terms of citation statistics.

%\stitle{Dynamic algorithms}.
Dynamic algorithms have proven useful for various tasks by avoiding computing from scratch~\cite{RamalingamR93}.
To our knowledge, little concern has been paid to dynamic scholarly article ranking except that~\cite{GhoshKHLL11} uses PageRank in dynamic citation networks. However, its solution is based on a strong and impractical assumption that there are no citations between articles in the same years.
Further, although there exist several studies on incremental PageRank computation~\cite{DesikanPSK05,AbiteboulPC03,WuR09} and on incremental PageRank approximation \cite{BahmaniCG10,BahmaniKMU12}, they are not designed for scholarly article ranking.
%
In this work, we study dynamic scholarly article ranking in the general setting by eliminating the strong and impractical assumption, and our incremental algorithm
is designed for the block-wise algorithm of Time-Weighted PageRank, and it is based on the citation characteristics, which has never been exploited before.
%Different from previous work, we study scholarly article ranking in a dynamic environment in terms of the citation characteristics of scholarly articles, which has never been exploited before.
